Parsing Postfix log files

### 2007-12-03 doc/logparser.tex
Dealt with another couple of XXX items.

The \SMTPlong{}, originally defined in \RFC{}~821~\cite{RFC821} and updated
in \RFC{}~2821~\cite{RFC2821}, is used for transferring mail between the
sending and receiving \MTA{}\@.  It is a simple, human readable, plain text
protocol, making it quite easy to test and debug problems with it.  Despite
the simplicity many virus and/or spam sending programs fail to implement it
properly, so requiring strict adherence to the protocol specification is
beneficial in protecting against spam and viruses.\footnote{This violates
the principle of \textit{Be liberal in what you accept, and conservative in
what you send\/} from \RFC{}~760~\cite{rfc760}, but unfortunately that
principle was written in a friendlier time. XXX CARL WANTS ME TO SUGGEST A
NEW PRINCIPAL AND POSSIBLY AN APPENDIX OF SPAM RELATED ISSUES\@.}  A
typical \SMTP{} conversation resembles the following (the lines starting
with a three digit number are sent by the server, all other lines are sent
by the client):

@@

    \item GOTO 2.  XXX IMPROVE THIS, IT'S RUBBISH\@.

>>>>

The \SMTPlong{}, originally defined in \RFC{}~821~\cite{RFC821} and updated
in \RFC{}~2821~\cite{RFC2821}, is used for transferring mail between the
sending and receiving \MTA{}\@.  It is a simple, human readable, plain text
protocol, making it quite easy to test and debug problems with it.  Despite
the simplicity many virus and/or spam sending programs fail to implement it
properly, so requiring strict adherence to the protocol specification is
beneficial in protecting against spam and viruses.\footnote{This violates
the principle of \textit{Be liberal in what you accept, and conservative in
what you send\/} from \RFC{}~760~\cite{rfc760}, but unfortunately that
principle was written in a friendlier time.  Given the deluge of spam that
mail servers are subjected to daily, a more appropriate maxim could be:
\textit{Require strict adherence to \RFC{}~2821; implement the strongest
restrictions you can; relax the restrictions and adherence only when
legitimate mail is impeded.\/}  It's not as friendly, nor as catchy, but it
more accurately reflects the current situation.} A typical \SMTP{}
conversation resembles the following (the lines starting with a three digit
number are sent by the server, all other lines are sent by the client):

@@

    \item Repeat from step two; this will continue indefinitely unless an
        administrator intervenes and deletes the appropriate mails from the
        queue.
